The title

### 2024-10-06 05_Manuscript/manuscript.tex
fixed citations (some errors?)

\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%

@@

  \usepackage[english]{selnolig} % disable illegal ligatures

@@

\linenumbers
\usepackage{csquotes}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

Death is something each of us must learn to cope with, whether in
healthy ways or less so. These issues may be at front of mind for many
in light of the COVID-19 pandemic. Various existential philosophers and
psychologists have proposed ways in which we deal with the awareness of
death and the anxiety this awareness often causes. Psychoanalyst Erik
Erikson (1950) proposed that during mid-life one becomes acutely aware
of their oncoming death and is motivated to care for things which will
outlast themselves. He called this act of caring generativity. In \emph{The
Denial of Death}, philosopher Ernest Becker (1973) posits that humans
undertake immortality projects to curb their sense of vulnerability to
death. Similarly, psychiatrist Robert Jay Lifton (1979), a mentee of
Erikson, described the awareness of death as being ever present and
motivating us to create symbols, thereby allowing us to imagine
ourselves as symbolically immortalized. Existential psychiatrist Irvin
Yalom (2008) notes that many of his clients experiencing anxiety about
their death take comfort in ``rippling,'' the idea that one's lasting
effects on the world will ripple out and influence the world after they
have died.

@@

One of these bodies of thought, called symbolic immortality, was
originally theorized by Lifton (1979), who thought that awareness of
death drives a fundamental human desire for a sense of continuity
lasting beyond the lifespan. Essentially, humans are meaning-seeking
creatures, and throughout our lives, this search for meaning involves an
evolving psychological imagery of life and death. Death, or the
transient nature of life, threatens our search for meaning. Lifton
thought that if we could achieve what we believe to be some form of
immortality, we could overcome this loss of meaning, and the awareness
of death could instead drive an inner vitality (imagery associated with
connection, integrity, and movement). If this drive toward vitality is
lost, we are vulnerable to a psychic numbness or death-in-life (imagery
associated with separation, disintegration, and stasis). In Lifton's own
words, ``Death does indeed bring about biological and psychic
annihilation. But life includes symbolic perceptions of connections that
precede and outlast that annihilation'' (1979, p.~18).

Lifton (1979) proposed five modes of experience or ways of achieving
symbolic immortality: The biological (or biosocial) mode in which one
lives on through their genetic and sociocultural progeny, the creative
mode in which one's accomplishments and contribution outlast oneself,
the natural mode in which one feels they are a part of the broader
universe, the spiritual mode in which one seeks to transcend the
physical realm to a higher spiritual realm beyond death, and the mode of
experiential transcendence in which one experiences a phenomenological
state of flow. The experiential mode must occur in the context of at
least one of the other four to really be considered transcendent, but it
is thought to have a great capacity to bring about personal change.

@@

Though some avoidance of (or buffering against) death anxiety is thought
to be universal and has the potential to increase interpersonal
conflict, awareness of death through symbolic immortality may also have
potential as a positive force. In particular, it is thought to be an
underlying motive for what Erikson referred to as generativity.
Generativity is the seventh of eight proposed stages in Erikson's (1950)
theory of psychosocial development, which he associated with midlife and
described as ``the concern in establishing and guiding the next
generation'' (Erikson, 1963, p.~267). Little systematic research was
conducted on this subject until the 1980's. Kotre (1984) expanded on the
theory and proposed that the drive for generativity was related to a
motive to expand the sense of self beyond the lifetime, especially in
light of the fear of death.

McAdams and de St.~Aubin (1992) sought to formalize the study
of generativity as a multidimensional construct. Their seven components
of generativity include cultural demand, inner desire (for symbolic
immortality and community), concern (for the next generation), belief
(in the human species), commitment, action, and narration (of
generativity within one's life story). In addition to a quantitative
measure of generative concern (the Loyola Generativity Scale), they
developed a system for content analysis of autobiographical episodes
pertaining to generativity, and symbolic immortality is one of the five
themes they found. Here they define symbolic immortality as ``any
reference to leaving a legacy, having an enduring influence, or leaving
behind products that will outlive one's physical existence,'' a theme
clearly related to both Lifton's and Erikson's theories (Aust et al., 2022; McAdams \& St. Aubin, 1992, p. 1011).

(Aust et al., 2022; Mathews \& Kling, 1988)

(McAdams \& de St.~Aubin, 1992, p.~1011).

These research areas depend on the construct of symbolic immortality for
their theoretical frameworks, but few researchers have attempted to
systematically and quantitatively assess this construct. Two attempts
have been made to develop such a measurement: Drolet's (1990) Sense of
Symbolic Immortality Scale and Mathews and Kling (1988) measure of
symbolic immortality, based on an original questionnaire by Mathews and
Mister (1987).

Drolet (1990) developed the Sense of Symbolic Immortality Scale based on
Robert J. Lifton's theory of symbolic immortality and its five modes of
experience. Drolet studied 136 adults, ages 18-30 and 30-40, and
hypothesized that those in their 30's (established adults) would have a
greater sense of symbolic immortality than the young adults (18-30). The
measure is inherently subjective, not only by the nature of self-report,
but in that the scale seeks to measure what a person \emph{believes} and how
they \emph{feel} about these subjects. The scale as a whole had a high
internal consistency (\emph{\$\textbackslash alpha\$} = .91) and test-retest reliability
was \emph{r} = .97. Internal consistency of subscales for the five
theoretical modes of immortality was mixed. Of the five, spiritual
immortality was the most distinct from the scale as a whole and the
other subscales. Factor analysis showed three factors, mapping onto
biosocial, creative, and spiritual. The transcendent and natural items
may be closely related to biosocial.

Moving beyond the scale development itself (still Drolet 1990), SSI
correlated negatively with death anxiety (Templer's Death Anxiety Scale)
and had a strong (\emph{r} = .84) positive relationship with purpose in life
(Maholick's Purpose in Life Test). In interpreting the very strong
correlation, the author suggests that SSI is a broader construct than
Purpose in Life and the scale itself may be less prone to social
desirability effects than the PIL, although this had not been directly
tested. Age group was also related, with established adults having a
higher SSI, particularly in the biosocial and creative domains.

@@

Mathews and Mister (1987) also developed a scale pertaining to symbolic
immortality, sensation seeking, and psychic numbness in a study
including 400 adults. Experiential transcendence was operationalized as
something like Zuckerman's (1979) sensation seeking, which may not fully
capture the original intent (the experience of losing oneself). Items
were mapped onto five factors, and the five factors largely aligned with
Lifton's constructs. Although internal consistency was at least
acceptable for each factor, goodness of fit statistics are not reported.
Some studies have used a revised version of the scale by Mathews and
Kling (1988), who adapted it for a study on prosocial behavior in the
context of nonprofit volunteer motivation. They reported similar results
for their revised scale. The items on these scales seem to have more
face validity than the scale by Drolet, but some factors seem more
behavioral and unnecessarily specific: pertaining to one's religiosity
or biological children, whereas Lifton's theory allows for a broader
interpretation of these dimensions. The Nature and Creative factors seem
most useful and theoretically aligned with Lifton.

@@

\begin{itemize}
\tightlist
\item
  try running with outliers as well --\textgreater{} if differences: then talk
  about what is going on with the outlier people
\end{itemize}

\section{Assumptions -------------------------------------------------------------}\label{assumptions--}

\section{Linearity}\label{linearity}

random = rchisq(nrow(noout{[} , 37:97{]}), 7) fake = lm(random\textasciitilde.,
data=noout{[} , 37:97{]})

standardized = rstudent(fake) \{qqnorm(standardized) abline(0,1)\} \#seems
okay

\section{Normality}\label{normality}

hist(standardized, breaks=15) \#a little skewed but mostly centered on 0
and between -2 and 2 so okay

\section{Homog/s}\label{homogs}

fitvalues = scale(fake\$fitted.values) \{plot(fitvalues, standardized)
abline(0,0) abline(v = 0)\} \#some homogeneity issues but we'll accept it

write.csv(noout, file = ``sona\_data\_screened.csv'', row.names = F)
library(beepr) beep(sound = 5)

```

>>>>

\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

@@

@@

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

Death is something each of us must learn to cope with, whether in
healthy ways or less so. These issues may be at front of mind for many
in light of the COVID-19 pandemic. Various existential philosophers and
psychologists have proposed ways in which we deal with the awareness of
death and the anxiety this awareness often causes. Psychoanalyst Erik
Erikson (1950) proposed that during mid-life one becomes
acutely aware of their oncoming death and is motivated to care for
things which will outlast themselves. He called this act of caring
generativity. In \emph{The Denial of Death}, philosopher Ernest Becker
(\textbf{becker1973?}) posits that humans undertake immortality projects to curb
their sense of vulnerability to death. Similarly, psychiatrist Robert
Jay Lifton (\textbf{lifton1979?}), a mentee of Erikson, described the awareness
of death as being ever present and motivating us to create symbols,
thereby allowing us to imagine ourselves as symbolically immortalized.
Existential psychiatrist Irvin Yalom (\textbf{yalom2008?}) notes that many of
his clients experiencing anxiety about their death take comfort in
``rippling,'' the idea that one's lasting effects on the world will ripple
out and influence the world after they have died.

@@

One of these bodies of thought, called symbolic immortality, was
originally theorized by Lifton (\textbf{lifton1979?}), who thought that
awareness of death drives a fundamental human desire for a sense of
continuity lasting beyond the lifespan. Essentially, humans are
meaning-seeking creatures, and throughout our lives, this search for
meaning involves an evolving psychological imagery of life and death.
Death, or the transient nature of life, threatens our search for
meaning. Lifton thought that if we could achieve what we believe to be
some form of immortality, we could overcome this loss of meaning, and
the awareness of death could instead drive an inner vitality (imagery
associated with connection, integrity, and movement). If this drive
toward vitality is lost, we are vulnerable to a psychic numbness or
death-in-life (imagery associated with separation, disintegration, and
stasis). In Lifton's own words, ``Death does indeed bring about
biological and psychic annihilation. But life includes symbolic
perceptions of connections that precede and outlast that annihilation''
(\textbf{lifton1979?}).

Lifton (\textbf{lifton1979?}) proposed five modes of experience or ways of
achieving symbolic immortality: The biological (or biosocial) mode in
which one lives on through their genetic and sociocultural progeny, the
creative mode in which one's accomplishments and contribution outlast
oneself, the natural mode in which one feels they are a part of the
broader universe, the spiritual mode in which one seeks to transcend the
physical realm to a higher spiritual realm beyond death, and the mode of
experiential transcendence in which one experiences a phenomenological
state of flow. The experiential mode must occur in the context of at
least one of the other four to really be considered transcendent, but it
is thought to have a great capacity to bring about personal change.

@@

Though some avoidance of (or buffering against) death anxiety is thought
to be universal and has the potential to increase interpersonal
conflict, awareness of death through symbolic immortality may also have
potential as a positive force. In particular, it is thought to be an
underlying motive for what Erikson referred to as generativity.
Generativity is the seventh of eight proposed stages in Erikson's
(1950) theory of psychosocial development, which he associated
with midlife and described as ``the concern in establishing and guiding
the next generation'' (E. H. Erikson, 1963, p. 267). Little systematic research
was conducted on this subject until the 1980's. Kotre (1984)
expanded on the theory and proposed that the drive for generativity was
related to a motive to expand the sense of self beyond the lifetime,
especially in light of the fear of death.

McAdams and de St.~Aubin (1992) sought to formalize the study
of generativity as a multidimensional construct. Their seven components
of generativity include cultural demand, inner desire (for symbolic
immortality and community), concern (for the next generation), belief
(in the human species), commitment, action, and narration (of
generativity within one's life story). In addition to a quantitative
measure of generative concern (the Loyola Generativity Scale), they
developed a system for content analysis of autobiographical episodes
pertaining to generativity, and symbolic immortality is one of the five
themes they found. Here they define symbolic immortality as ``any
reference to leaving a legacy, having an enduring influence, or leaving
behind products that will outlive one's physical existence,'' a theme
clearly related to both Lifton's and Erikson's theories (McAdams \& St. Aubin, 1992, p. 1011).

These research areas depend on the construct of symbolic immortality for
their theoretical frameworks, but few researchers have attempted to
systematically and quantitatively assess this construct. Two attempts
have been made to develop such a measurement: Drolet's (1990)
Sense of Symbolic Immortality Scale and Mathews and Kling's
(1988) measure of symbolic immortality, based on an original
questionnaire by Mathews and Mister (1987).

Drolet (1990) developed the Sense of Symbolic Immortality Scale
based on Robert J. Lifton's theory of symbolic immortality and its five
modes of experience. Drolet studied 136 adults, ages 18-30 and 30-40,
and hypothesized that those in their 30's (established adults) would
have a greater sense of symbolic immortality than the young adults
(18-30). The measure is inherently subjective, not only by the nature of
self-report, but in that the scale seeks to measure what a person
\emph{believes} and how they \emph{feel} about these subjects. The scale as a
whole had a high internal consistency (\(\alpha\) = .91) and test-retest
reliability was \emph{r} = .97. Internal consistency of subscales for the
five theoretical modes of immortality was mixed. Of the five, spiritual
immortality was the most distinct from the scale as a whole and the
other subscales. Factor analysis showed three factors, mapping onto
biosocial, creative, and spiritual. The transcendent and natural items
may be closely related to biosocial.

Moving beyond the scale development itself, SSI correlated negatively
with Templer's Death Anxiety Scale and had a strong (\emph{r} = .84) positive
relationship with Maholick's Purpose in Life Test (Drolet, 1990). In
interpreting the very strong correlation, the author suggests that SSI
is a broader construct than Purpose in Life and the scale itself may be
less prone to social desirability effects than the PIL, although this
had not been directly tested. Age group was also related, with
established adults having a higher SSI, particularly in the biosocial
and creative domains.

@@

Mathews and Mister (1987) also developed a scale pertaining to
symbolic immortality, sensation seeking, and psychic numbness in a study
including 400 adults. Experiential transcendence was operationalized as
similar to Zuckerman's (1979) sensation seeking, which may
not fully capture the original intent (the experience of losing
oneself). Items were mapped onto five factors, and the five factors
largely aligned with Lifton's constructs. Although internal consistency
was at least acceptable for each factor, goodness of fit statistics are
not reported. Some studies have used a revised version of the scale by
Mathews and Kling (1988), who adapted it for a study on
prosocial behavior in the context of nonprofit volunteer motivation.
They reported similar results for their revised scale. The items on
these scales seem to have more face validity than the scale by Drolet,
but some factors seem more behavioral and unnecessarily specific:
pertaining to one's religiosity or biological children, whereas Lifton's
theory allows for a broader interpretation of these dimensions. The
Nature and Creative factors seem most useful and theoretically aligned
with Lifton.

@@

\begin{verbatim}
## [1] 352
\end{verbatim}

\begin{verbatim}
## [1] 353
\end{verbatim}

\begin{verbatim}
## [1] 326
\end{verbatim}

\begin{verbatim}
## [1] 326
\end{verbatim}

\subsection{EFA}\label{efa}

\subsubsection{Number of Factors}\label{number-of-factors}

also do five

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}

\begin{verbatim}
## Parallel analysis suggests that the number of factors =  7  and the number of components =  NA
\end{verbatim}

\begin{verbatim}
## [1] 5
\end{verbatim}

\begin{verbatim}
## [1] 7
\end{verbatim}

\subsubsection{Simple Structure}\label{simple-structure}

\begin{verbatim}
## Factor Analysis using method =  ml
## Call: fa(r = efaDF, nfactors = 2, rotate = "oblimin", fm = "ml")
## Standardized loadings (pattern matrix) based upon correlation matrix
##         ML1   ML2    h2   u2 com
## Q2_1   0.57  0.15 0.436 0.56 1.1
## Q2_2   0.77 -0.05 0.552 0.45 1.0
## Q2_3   0.76 -0.08 0.528 0.47 1.0
## Q2_4   0.70  0.05 0.523 0.48 1.0
## Q2_5   0.73 -0.10 0.466 0.53 1.0
## Q2_6   0.72  0.06 0.561 0.44 1.0
## Q2_7   0.47  0.07 0.259 0.74 1.0
## Q2_8   0.65 -0.03 0.408 0.59 1.0
## Q2_9   0.63  0.01 0.405 0.60 1.0
## Q2_10  0.58 -0.05 0.308 0.69 1.0
## Q2_11  0.18  0.64 0.546 0.45 1.2
## Q2_12 -0.05  0.92 0.805 0.19 1.0
## Q2_13  0.11  0.18 0.066 0.93 1.6
## Q2_14  0.66  0.06 0.480 0.52 1.0
## Q2_15  0.68 -0.08 0.421 0.58 1.0
## Q2_16  0.79 -0.08 0.571 0.43 1.0
## Q2_17 -0.01  0.92 0.836 0.16 1.0
## Q2_18  0.14  0.75 0.686 0.31 1.1
## Q2_19  0.46  0.12 0.286 0.71 1.1
## Q2_20  0.64 -0.11 0.354 0.65 1.1
## Q4_1   0.71 -0.06 0.468 0.53 1.0
## Q4_2   0.60 -0.05 0.328 0.67 1.0
## Q4_3   0.60 -0.06 0.335 0.66 1.0
## Q4_4   0.52  0.13 0.351 0.65 1.1
## Q4_5   0.67 -0.06 0.410 0.59 1.0
## Q4_6   0.52  0.19 0.411 0.59 1.3
## Q4_7   0.31 -0.13 0.073 0.93 1.3
## Q4_8   0.34  0.07 0.148 0.85 1.1
## Q4_9   0.65  0.15 0.533 0.47 1.1
## Q4_10  0.68  0.03 0.481 0.52 1.0
## Q4_11  0.09  0.14 0.042 0.96 1.7
## Q4_12  0.40 -0.04 0.146 0.85 1.0
## Q4_13  0.23  0.38 0.286 0.71 1.7
## Q4_14  0.17  0.46 0.317 0.68 1.3
## Q4_15  0.63  0.04 0.421 0.58 1.0
## Q4_16  0.55  0.01 0.312 0.69 1.0
## Q4_17  0.12  0.51 0.336 0.66 1.1
## Q4_18  0.10  0.19 0.064 0.94 1.5
## Q4_19 -0.07  0.95 0.834 0.17 1.0
## Q5_1   0.07  0.78 0.670 0.33 1.0
## Q5_2   0.02  0.85 0.740 0.26 1.0
## Q5_3   0.09  0.50 0.305 0.70 1.1
## Q5_4   0.51  0.25 0.446 0.55 1.5
## Q5_5   0.14  0.00 0.021 0.98 1.0
## Q5_6   0.44  0.16 0.290 0.71 1.3
## Q5_7   0.59 -0.01 0.338 0.66 1.0
## Q5_8   0.68  0.04 0.491 0.51 1.0
## Q5_9   0.75 -0.03 0.547 0.45 1.0
## Q5_10 -0.06  0.85 0.669 0.33 1.0
## Q5_11 -0.02  0.15 0.020 0.98 1.0
## Q5_12  0.05  0.30 0.107 0.89 1.1
## Q5_13  0.74  0.04 0.574 0.43 1.0
## Q5_14  0.31 -0.04 0.085 0.91 1.0
## Q5_15  0.57  0.09 0.387 0.61 1.1
## Q5_17  0.49  0.15 0.334 0.67 1.2
## Q5_18  0.35  0.20 0.232 0.77 1.6
## Q5_19  0.52  0.25 0.466 0.53 1.4
## Q5_20  0.19 -0.06 0.029 0.97 1.2
## 
##                         ML1  ML2
## SS loadings           14.91 7.63
## Proportion Var         0.26 0.13
## Cumulative Var         0.26 0.39
## Proportion Explained   0.66 0.34
## Cumulative Proportion  0.66 1.00
## 
##  With factor correlations of 
##      ML1  ML2
## ML1 1.00 0.49
## ML2 0.49 1.00
## 
## Mean item complexity =  1.1
## Test of the hypothesis that 2 factors are sufficient.
## 
## df null model =  1653  with the objective function =  38.9 with Chi Square =  12870.73
## df of  the model are 1538  and the objective function was  12.63 
## 
## The root mean square of the residuals (RMSR) is  0.07 
## The df corrected root mean square of the residuals is  0.07 
## 
## The harmonic n.obs is  352 with the empirical chi square  5082.08  with prob <  0 
## The total n.obs was  352  with Likelihood Chi Square =  4161.82  with prob <  4.3e-240 
## 
## Tucker Lewis Index of factoring reliability =  0.747
## RMSEA index =  0.07  and the 90 % confidence intervals are  0.067 0.072
## BIC =  -4856.44
## Fit based upon off diagonal values = 0.96
## Measures of factor score adequacy             
##                                                    ML1  ML2
## Correlation of (regression) scores with factors   0.98 0.98
## Multiple R square of scores with factors          0.96 0.96
## Minimum correlation of possible factor scores     0.93 0.93
\end{verbatim}

\begin{verbatim}
## Factor Analysis using method =  ml
## Call: fa(r = efaDF %>% select(efa_loadings %>% filter(keep == "yes") %>% 
##     pull(question)), nfactors = 2, rotate = "oblimin", fm = "ml")
## Standardized loadings (pattern matrix) based upon correlation matrix
##         ML1   ML2    h2   u2 com
## Q2_1   0.57  0.15 0.435 0.56 1.1
## Q2_2   0.77 -0.06 0.551 0.45 1.0
## Q2_3   0.76 -0.08 0.529 0.47 1.0
## Q2_4   0.69  0.06 0.525 0.47 1.0
## Q2_5   0.73 -0.10 0.467 0.53 1.0
## Q2_6   0.72  0.06 0.561 0.44 1.0
## Q2_7   0.47  0.07 0.260 0.74 1.0
## Q2_8   0.65 -0.02 0.408 0.59 1.0
## Q2_9   0.63  0.01 0.406 0.59 1.0
## Q2_10  0.58 -0.05 0.306 0.69 1.0
## Q2_11  0.18  0.64 0.545 0.45 1.2
## Q2_12 -0.05  0.92 0.805 0.20 1.0
## Q2_14  0.66  0.05 0.477 0.52 1.0
## Q2_15  0.68 -0.08 0.422 0.58 1.0
## Q2_16  0.79 -0.08 0.572 0.43 1.0
## Q2_17 -0.01  0.92 0.837 0.16 1.0
## Q2_18  0.14  0.75 0.686 0.31 1.1
## Q2_19  0.46  0.13 0.287 0.71 1.1
## Q2_20  0.64 -0.10 0.353 0.65 1.0
## Q4_1   0.71 -0.06 0.469 0.53 1.0
## Q4_2   0.60 -0.06 0.329 0.67 1.0
## Q4_3   0.60 -0.05 0.335 0.67 1.0
## Q4_4   0.52  0.13 0.349 0.65 1.1
## Q4_5   0.67 -0.06 0.410 0.59 1.0
## Q4_6   0.52  0.20 0.413 0.59 1.3
## Q4_7   0.31 -0.13 0.072 0.93 1.4
## Q4_8   0.34  0.07 0.146 0.85 1.1
## Q4_9   0.65  0.14 0.533 0.47 1.1
## Q4_10  0.68  0.02 0.481 0.52 1.0
## Q4_12  0.40 -0.04 0.145 0.86 1.0
## Q4_13  0.23  0.38 0.285 0.72 1.7
## Q4_14  0.16  0.47 0.321 0.68 1.2
## Q4_15  0.63  0.04 0.423 0.58 1.0
## Q4_16  0.55  0.01 0.309 0.69 1.0
## Q4_17  0.12  0.51 0.329 0.67 1.1
## Q4_19 -0.07  0.95 0.835 0.16 1.0
## Q5_1   0.07  0.78 0.672 0.33 1.0
## Q5_2   0.02  0.85 0.742 0.26 1.0
## Q5_3   0.08  0.51 0.306 0.69 1.1
## Q5_4   0.51  0.25 0.446 0.55 1.5
## Q5_6   0.44  0.16 0.288 0.71 1.2
## Q5_7   0.59 -0.02 0.337 0.66 1.0
## Q5_8   0.68  0.04 0.489 0.51 1.0
## Q5_9   0.75 -0.02 0.549 0.45 1.0
## Q5_10 -0.06  0.85 0.666 0.33 1.0
## Q5_13  0.74  0.04 0.574 0.43 1.0
## Q5_14  0.31 -0.04 0.085 0.91 1.0
## Q5_15  0.57  0.09 0.388 0.61 1.1
## Q5_17  0.49  0.15 0.334 0.67 1.2
## Q5_18  0.35  0.20 0.230 0.77 1.6
## Q5_19  0.52  0.25 0.466 0.53 1.4
## 
##                         ML1  ML2
## SS loadings           14.80 7.39
## Proportion Var         0.29 0.14
## Cumulative Var         0.29 0.44
## Proportion Explained   0.67 0.33
## Cumulative Proportion  0.67 1.00
## 
##  With factor correlations of 
##      ML1  ML2
## ML1 1.00 0.49
## ML2 0.49 1.00
## 
## Mean item complexity =  1.1
## Test of the hypothesis that 2 factors are sufficient.
## 
## df null model =  1275  with the objective function =  35.47 with Chi Square =  11817.61
## df of  the model are 1174  and the objective function was  9.54 
## 
## The root mean square of the residuals (RMSR) is  0.06 
## The df corrected root mean square of the residuals is  0.06 
## 
## The harmonic n.obs is  352 with the empirical chi square  2962.25  with prob <  4.6e-155 
## The total n.obs was  352  with Likelihood Chi Square =  3164.31  with prob <  3.7e-182 
## 
## Tucker Lewis Index of factoring reliability =  0.794
## RMSEA index =  0.069  and the 90 % confidence intervals are  0.067 0.072
## BIC =  -3719.59
## Fit based upon off diagonal values = 0.98
## Measures of factor score adequacy             
##                                                    ML1  ML2
## Correlation of (regression) scores with factors   0.98 0.98
## Multiple R square of scores with factors          0.96 0.96
## Minimum correlation of possible factor scores     0.93 0.93
\end{verbatim}

\begin{verbatim}
## Factor Analysis using method =  ml
## Call: fa(r = efaDF, nfactors = 3, rotate = "oblimin", fm = "ml")
## Standardized loadings (pattern matrix) based upon correlation matrix
##         ML1   ML2   ML3    h2   u2 com
## Q2_1   0.47  0.17  0.20 0.445 0.56 1.6
## Q2_2   0.63 -0.03  0.28 0.572 0.43 1.4
## Q2_3   0.72 -0.05  0.08 0.528 0.47 1.0
## Q2_4   0.71  0.09 -0.04 0.548 0.45 1.0
## Q2_5   0.74 -0.07 -0.04 0.495 0.51 1.0
## Q2_6   0.64  0.09  0.16 0.560 0.44 1.2
## Q2_7   0.59  0.10 -0.26 0.371 0.63 1.4
## Q2_8   0.74  0.01 -0.18 0.500 0.50 1.1
## Q2_9   0.72  0.04 -0.18 0.492 0.51 1.1
## Q2_10  0.39 -0.04  0.40 0.395 0.61 2.0
## Q2_11  0.14  0.64  0.06 0.546 0.45 1.1
## Q2_12 -0.06  0.92  0.02 0.804 0.20 1.0
## Q2_13 -0.06  0.18  0.37 0.179 0.82 1.5
## Q2_14  0.45  0.07  0.45 0.588 0.41 2.0
## Q2_15  0.62 -0.05  0.11 0.418 0.58 1.1
## Q2_16  0.75 -0.04  0.07 0.573 0.43 1.0
## Q2_17  0.00  0.92 -0.02 0.837 0.16 1.0
## Q2_18  0.13  0.76  0.02 0.686 0.31 1.1
## Q2_19  0.53  0.15 -0.15 0.338 0.66 1.3
## Q2_20  0.71 -0.07 -0.14 0.420 0.58 1.1
## Q4_1   0.75 -0.02 -0.09 0.517 0.48 1.0
## Q4_2   0.60 -0.03  0.00 0.340 0.66 1.0
## Q4_3   0.64 -0.03 -0.07 0.367 0.63 1.0
## Q4_4   0.40  0.15  0.23 0.371 0.63 1.9
## Q4_5   0.54 -0.04  0.25 0.425 0.57 1.4
## Q4_6   0.58  0.22 -0.13 0.459 0.54 1.4
## Q4_7   0.07 -0.13  0.51 0.270 0.73 1.2
## Q4_8   0.19  0.08  0.32 0.208 0.79 1.8
## Q4_9   0.54  0.17  0.21 0.539 0.46 1.5
## Q4_10  0.52  0.05  0.33 0.522 0.48 1.7
## Q4_11 -0.12  0.13  0.45 0.212 0.79 1.3
## Q4_12  0.42 -0.01 -0.06 0.161 0.84 1.0
## Q4_13  0.20  0.39  0.07 0.287 0.71 1.6
## Q4_14  0.23  0.48 -0.14 0.346 0.65 1.6
## Q4_15  0.66  0.07 -0.07 0.451 0.55 1.0
## Q4_16  0.30  0.01  0.54 0.497 0.50 1.6
## Q4_17  0.00  0.51  0.25 0.381 0.62 1.4
## Q4_18 -0.17  0.18  0.55 0.326 0.67 1.4
## Q4_19 -0.05  0.95 -0.06 0.837 0.16 1.0
## Q5_1   0.07  0.78  0.00 0.670 0.33 1.0
## Q5_2   0.04  0.85 -0.04 0.744 0.26 1.0
## Q5_3   0.09  0.51  0.00 0.305 0.69 1.1
## Q5_4   0.50  0.28  0.00 0.453 0.55 1.6
## Q5_5   0.13  0.01  0.03 0.021 0.98 1.1
## Q5_6   0.33  0.17  0.24 0.313 0.69 2.4
## Q5_7   0.46  0.01  0.25 0.356 0.64 1.5
## Q5_8   0.49  0.06  0.41 0.568 0.43 2.0
## Q5_9   0.70  0.01  0.08 0.544 0.46 1.0
## Q5_10 -0.09  0.84  0.05 0.671 0.33 1.0
## Q5_11 -0.09  0.15  0.15 0.042 0.96 2.7
## Q5_12 -0.17  0.29  0.46 0.294 0.71 2.0
## Q5_13  0.61  0.07  0.25 0.583 0.42 1.4
## Q5_14  0.21 -0.03  0.21 0.107 0.89 2.0
## Q5_15  0.62  0.12 -0.10 0.431 0.57 1.1
## Q5_17  0.46  0.17  0.04 0.335 0.66 1.3
## Q5_18  0.29  0.21  0.12 0.233 0.77 2.2
## Q5_19  0.44  0.27  0.17 0.468 0.53 2.0
## Q5_20  0.20 -0.06 -0.02 0.032 0.97 1.2
## 
##                         ML1  ML2  ML3
## SS loadings           13.39 7.95 3.65
## Proportion Var         0.23 0.14 0.06
## Cumulative Var         0.23 0.37 0.43
## Proportion Explained   0.54 0.32 0.15
## Cumulative Proportion  0.54 0.85 1.00
## 
##  With factor correlations of 
##      ML1  ML2  ML3
## ML1 1.00 0.45 0.32
## ML2 0.45 1.00 0.23
## ML3 0.32 0.23 1.00
## 
## Mean item complexity =  1.4
## Test of the hypothesis that 3 factors are sufficient.
## 
## df null model =  1653  with the objective function =  38.9 with Chi Square =  12870.73
## df of  the model are 1482  and the objective function was  10.58 
## 
## The root mean square of the residuals (RMSR) is  0.05 
## The df corrected root mean square of the residuals is  0.05 
## 
## The harmonic n.obs is  352 with the empirical chi square  3147.43  with prob <  7.2e-122 
## The total n.obs was  352  with Likelihood Chi Square =  3478.38  with prob <  1.2e-161 
## 
## Tucker Lewis Index of factoring reliability =  0.8
## RMSEA index =  0.062  and the 90 % confidence intervals are  0.059 0.065
## BIC =  -5211.52
## Fit based upon off diagonal values = 0.98
## Measures of factor score adequacy             
##                                                    ML1  ML2  ML3
## Correlation of (regression) scores with factors   0.98 0.98 0.92
## Multiple R square of scores with factors          0.96 0.96 0.84
## Minimum correlation of possible factor scores     0.92 0.93 0.68
\end{verbatim}
